Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
we explicitly state we want a controller that does not saturate

\begin{myassumption}
%
The controller and the plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows, ADC/DAC nonlinearities) will be disregarded.
\red{should we explicitly state we want a controller that does not saturate?}
%
\end{myassumption}

>>>>

\begin{myassumption}
%
The controller and the plant are linear, {\it i.e.}, any source of nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will be disregarded.
%
\end{myassumption}
